Modalities for Location Virtualization

### 2022-09-18 soundness.tex
moreless the structure is fine: now fill in the gaps

\begin{assumption}
\label{assumption}
  Iris defines a certain piece of ghost state,
  defines a predicate $\genheapinterp\store$
  that ties a store~$\store$ to this ghost state,
  and defines the points-to assertion $\loc\fpointsto\qv\blk$
  in terms of this ghost state.
  This is visible in the paper~\cite[\S6.3.2]{iris}
  and in Iris's \texttt{gen\_heap} library~\cite{genheap}.
  %
  We re-use this machinery without change,
  so we do not repeat these definitions.
  We mention the predicate $\genheapinterp\!$
  in our own invariant (Definition~\ref{def:invariant}),
  where it is applied to the \logical store~$\logicalstore$.
\end{assumption}

>>>>

\begin{assumption}
\label{assumption}
  Iris defines a certain piece of ghost state,
  defines a predicate $\genheapinterp\store$
  that ties a store~$\store$ to this ghost state,
  and defines the points-to assertion $\loc\fpointsto\qv\blk$
  in terms of this ghost state.
  This is visible in the paper~\cite[\S6.3.2]{iris}
  and in Iris's \texttt{gen\_heap} library~\cite{genheap}.
  %
  We re-use this machinery without change,
  so we do not repeat these definitions.
  We mention the predicate $\genheapinterp\!$
  in our own invariant (Definition~\ref{def:invariant}),
  where it is applied to the \logical store~$\store$.
\end{assumption}
